A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-04-08 paper/paper.Rnw
Add setup chunk, fix author formatting

@@

\title{A Convolutional Neural Network for Outsole Recognition}

@@

% or include affiliations in footnotes:
\author[mymainaddress]{Miranda Tilton}

\author[mymainaddress]{Susan Vanderplas\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead[url]{https://forensicstats.org}
\ead{srvander@iastate.edu}

\address[mymainaddress]{Statistics Department, Iowa State University}

>>>>

<<setup, include = F>>=
knitr::opts_chunk$set(echo = F, dev = "pdf", dpi = 1000)
@

@@

\title{A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}}
\tnotetext[t1]{This document is the results of the research
project funded ....}

@@

% or include affiliations in footnotes:
\author[1]{Miranda Tilton\fnref{isu}}
\ead{tiltonm@iastate.edu}

\author[1]{Susan Vanderplas\corref{cor1}\fnref{isu}}
\cortext[cor1]{Corresponding author}
\ead{srvander@iastate.edu}

\address[1]{195 Durham Center, 613 Morill Rd, Ames, IA 50010}
\fntext[isu]{Center for Statistical Applications in Forensic Evidence, Iowa State University}
